### 2022-05-30 main/chapter_2ljets.tex
omega to sigma

Uncertainty in $\ptmiss$ is modelled for $\metsig$ by a covariance matrix
$\Omega$ in the transverse plane, and used to define
\begin{equation}
\metsig^2
=
\ptmiss \Omega^{-1} \ptmiss
=
\frac{(\met)^2}{\sigma_L^2(1 - \rho_{LT}^2)}
,
\end{equation}
in which $\sigma_L^2$ is the variance in the direction of $\ptmiss$ and
$\rho_{LT}$ is the correlation coefficient between the parallel and
perpendicular components~\cite{atlas_met_significance}.
This is the square of a Mahalanobis (standard-deviations) distance between
the origin and $\ptmiss$~\cite{mahalanobis1936generalised}.

Just as $\ptmiss$ is constructed from a (negative) sum of contributions from
objects in an event,
$\Omega$ is a sum of covariances assigned to those objects;
both means and variances add linearly.

>>>>

Uncertainty in $\ptmiss$ is modelled for $\metsig$ by a covariance matrix
$\Sigma$ in the transverse plane, and used to define
\begin{equation}
\metsig^2
=
\ptmiss \Sigma^{-1} \ptmiss
=
\frac{(\met)^2}{\sigma_L^2(1 - \rho_{LT}^2)}
,
\end{equation}
in which $\sigma_L^2$ is the variance in the direction of $\ptmiss$ and
$\rho_{LT}$ is the correlation coefficient between the parallel and
perpendicular components~\cite{atlas_met_significance}.
This is the square of a Mahalanobis (standard-deviations) distance between
the origin and $\ptmiss$~\cite{mahalanobis1936generalised}.

Just as $\ptmiss$ is constructed from a (negative) sum of contributions from
objects in an event,
$\Sigma$ is a sum of covariances assigned to those objects;
both means and variances add linearly.
